Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1) \note{\scriptsize Authors, please add/check middle initials and affiliations}

### 2014-04-16 WSSSPE1_report/WSSSPE1_summary_report.tex
work on conclusions

\todo{pull the discussion together}

\todo{add some analysis of the deficiencies and difficulties that are
  present in different fields, and those that are common?}

\todo{say something about licensing - lessons, advice, etc.?}

@@

@@

\note{if needed.}

\subsection{Follow up actions}

\note{or at least the discussion about them, and the current plans for
  future events.}

\note{conclusions from pre-workshop paper follows}

The WSSSPE workshop has begun an experiment in how we can
collaboratively build a workshop agenda. However, contributors also
want to get credit for their participation in the process. And the
workshop organizers want to make sure that the workshop content and
their efforts are recorded.  Ideally, there would be a service that
would be able to index the contributions to the workshop, serving the
authors, the organizers, and the larger community. But since there
isn't such a service today, the workshop organizers are writing this
initial report and making use of arXiv as a partial solution to
provide a record of the workshop.

After the workshop, one or more additional papers will be created that
will include the discussions at the workshop. These papers will likely
have many authors, and may be submitted to peer-reviewed journals.

\katznote{discuss sustainability survey}

>>>>

\note{add some analysis of the deficiencies and difficulties that are
  present in different fields, and those that are common?}

\note{say something about licensing - lessons, advice, etc.?}

@@

\todo{what are the main issues discussed in each discussion section?, and what are the main common issues from the cross-cutting section - Dan to do that latter part}

@@

\note{lessons from the 3 discussion sessions go here, and lessons from the cross-cutting section as well?}

\subsubsection{Workshop process}

The WSSSPE workshop can be viewed as an experiment in how we can
collaboratively and inclusively build a workshop agenda, without asking
large numbers of people to submit papers that will be rejected so that the
workshop can have a low acceptance rate.

Contributors also want to get credit for their participation in the process.
And the workshop organizers want to make sure that the workshop content and
their efforts are recorded.  The methods used in the WSSSPE1 workshop
were successful; we had good participation, many contributors have a
report they can cite, and the record of the workshop is open and available,
through the self-published reports, the workshop web site and notes site,
and this paper.  In addition, many additional papers are being created that
will include the discussions at the workshop, including extended versions
of many of the self published reports. such as those that are in this
special issue.

Ideally, there would be a service that
would be able to index the contributions to the workshop, serving the
authors, the organizers, and the larger community.

\subsection{Future activities}

The organizers of the workshop have begun a survey to understand how
the community define software sustainability.  It is expected that this survey
will gather one or more consensus definitions, and lead to a short paper
discussing them, as well as the level of consensus.

Additional activities that are being planned include
two additional WSSSPE workshops at the 2014 SciPy and SC14 conferences.
The SciPy workshop (WSSSPE1.1) will focus on how some software projects
from the SciPy community have dealt with software sustainability issues, both
successfully and unsuccessfully, while the SC14 workshop (WSSSPE2) will
be more general, and will likely focus on determining and publicizing specific
activities that the overall scientific software community can take to move forward.
In addition, there will be a minisymposium on ``Reliable Computational Science''
at the 2014 Society for Industrial and Applied Mathematics (SIAM)
Annual Meeting (SIAM AN14, http://meetings.siam.org)
to further explore some of the key issues raised in
WSSSPE .
